Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2023-05-31 docs/manuscript/manuscript.tex
Updates from Overleaf

\usepackage{doi}
\usepackage{natbib}
\bibliographystyle{chicago}
\setcitestyle{authoryear,open={(},close={)}}
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty

@@

\begin{abstract}
While the number of reproduction and replication studies undertaken in the social and behavioral sciences continues to rise, such studies have not yet become commonplace in geography. 
Existing attempts to reproduce geographic research suggest that many studies cannot be fully reproduced, or are simply missing components needed to attempt a reproduction. 
Despite this suggestive evidence, we have not yet systematically assessed geographers' perceptions of reproducibility or the use of reproducible research practices across the discipline's diverse research traditions; nor have we identified the factors that keep geographers from conducting more reproduction studies.
We address each of these questions by surveying active geographic researchers selected using probability sampling techniques from a rigorously constructed sampling frame.
Our results identify a clear division in perception of reproducibility among geographic sub-fields. 
We also find varying levels of familiarity with reproducible research practices and a perceived lack of incentives to attempt and publish reproduction studies. 
Despite many barriers to reproducibility and divisions between subfields, we also find common foundations for examining and expanding reproducibility in the field.
These include interest in publishing transparent and reproducible methods, and in reproducing other researchers' studies for a variety of motivations including learning, checking the validity of a prior study, or extending the prior study.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Introduction}
Reproducible research publicly discloses the evidence used to support claims made in prior work, facilitates the independent verification of those claims, and the extension of that work by the broader research community \citep{earp2015, nosek2012scientific, Schmidt2009}.
While reproducibility is not a guarantee of scientific or practical usefulness, it does provide a strong basis for the collective evaluation of ideas.
Nonetheless, systematic reviews \citep{moraila2014measuring, iqbal2016reproducible} of published research papers reveal a lack of data and code for reproducibility  and attempts to reproduce published research papers \citep{raghupathi2022reproducibility, chang2015economics} frequently fail.
Previous studies consistently link the irreproducibility of research to inadequate record keeping, opaque reporting, the inaccessibility of research components, and a lack of incentives to share research details or to attempt reproduction studies \citep{ranstam2000fraud, anderson2007normative, NASEM2019}.
Surveys of researchers find that few researchers are attempting to independently reproduce the work of others \citep{baker20161, boulbes2018survey}.
At the same time, a sizable portion of researchers admit engaging in questionable research practices tied to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.

Despite these concerns, the available literature currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically.
This knowledge gap exists because researchers conducting reproducibility assessments, surveys of researcher practices, and reproduction attempts have not defined clear target populations for inference, or used probability sampling techniques structured by well-defined sampling frames that support generalization \citep{NASEM2019}.
Attempts to reproduce past results typically focus on recreating the results of one or a small number of studies selected based on topical interest or researcher familiarity \citep{camerer2016evaluating, camerer2018evaluating, open2015estimating}. 
Attempts to catalog or survey reproducible research practices have drawn samples of research papers from archives such as conference paper series, specific journals, or disciplinary repositories \citep{byrne_2017, gundersen2018state, stodden2016enhancing, stodden2018enabling}, or have drawn samples of researchers from specific journals, members of professional associations, or conference attendees \citep{baker20161}.
These samples are convenient, but are not guaranteed to be representative of researchers and research activity in a particular field. 
Surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response, which further complicates their evaluation and use. 
Finally, both reproduction attempts and reproducibility surveys have focused on evaluating the computational components of past studies such as data and code availability rather than all aspects of research design and execution.

Reproducibility surveys and reproduction attempts in the geographic literature face these same challenges. 
The few available reproducibility surveys in the discipline have relied on convenience samples drawn from specialist conferences and have only focused on computationally intensive forms of geographic research \citep{balz2020reproducibility, konkol2019, ostermann2017}. 
The small number of published attempts to reproduction geographic research similarly have focused on the computational reproducibility of conference papers \citep{Nust-AGILE_2018, Nust_AGILE_2020, Nust_AGILE_2021, Nust_AGILE_2022, ostermann2021,} or on specific topics such as COVID-19 \citep{Holler2023disability, Kedron2022dimaggio, Kedron2023Beyond, paez2022reproducibility}. 
More recent reproduction attempts by \citet{Kedron2023Beyond} show that the factors hindering the recreation of results and the evaluation of claims likely extend beyond computation into the conceptualization and design of geographic research.

Geographers continue to debate the role of reproduction studies in the discipline \citep{brunsdon2016, goodchild2021Annals, kedron2022replication, kedron2021IJGIS, singleton2016, sui2021, Wainwright2021}, examine the reproducibility of individual studies \citep{Nust_AGILE_2022, ostermann2021}, and build the infrastructure needed to support reproducible research \citep{nust2019, wilson2021, yin2019cybergis}. 
And yet, we still have not systematically assessed the use of reproducible research practices across the discipline's diverse research traditions, or identified the factors that have hindered geographers from adopting reproducible research practices and conducting reproduction studies. 
Without answers to these questions it is unclear what actions geographers should take if they wish to improve the reproducibility of work in the discipline.

To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of reproducibility, perception of reproducibility in their sub-fields,  familiarity and use of reproducible research practices, and the factors they see as barriers to reproducible research.
To support generalization, we used a probability sampling scheme designed to capture the breadth of geographic research.
In the remainder of this paper, we first present the design of our survey, sampling strategy, and analytical approach. 
We then present the results of our survey, first focusing on researcher perceptions and use of reproducible research practices, and then analyzing researcher experiences attempting to reproduce prior work. 
Finally, we discuss the implications of our survey results and conclude by presenting a snapshot of geographic researcher perceptions of reproducibility and where the discipline may go from here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data and Methods}
Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Reproducibility in Geographic Research Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
The OSF repository connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
All of the results presented in this paper can be independently reproduced using the materials in that repository.
We encourage interested readers to critically evaluate and build on these materials through their own work.
Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.

@@

First, beginning at the publication level, we identified journals indexed as either geography or physical geography by the \href{https://access.clarivate.com/}{Web of Science's Journal Citation Reports} that also had a 5-year impact factor greater than 1.5.
From those journals, we created a database of all articles published between 2017 and 2021.

Second, we used Arizona State University's institutional subscription to the \href{https://www.scopus.com/home.uri}{Scopus Database} to extract journal information (e.g., subject area, ranking), article information (e.g., abstract, citation counts), and author information (e.g., corresponding status, email) for each publication. 
Because our intention was to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = ``Article''} and removed all other publication types (e.g., editorials, book reviews) from our article database. 
We also removed articles with missing authorship information.

Third, we created a list of researchers and their published articles, focusing on corresponding authors for two reasons.
(1) Corresponding authorship is one indicator of the level of involvement an individual had in a given work. 
While imperfect, it was the best available indicator in the Scopus database as across journals there is no commonly adopted policy for declarations of author work (e.g., CRediT Statements).
(2) Scopus maintains email contact information for all corresponding authors, which gave us a means of contacting researchers in our sampling frame.
Scopus also maintains a unique identifier for each author (author-id) across time, which allowed us to identify authors across publications.

Fourth, we constructed a sampling frame of unique researchers and their most recent email contact information. 
We determined uniqueness by grouping researchers by their author-id, and we determined the most recent contact information by selecting records associated with the most recent year of publication. 
For 383 researchers who had two or more distinct emails in the latest year of publication, we removed non-institutional personal email addresses and then selected one of the remaining institutional email address.

Applying these criteria yielded a sampling frame of 29,828 researchers. 
On average, these authors published 2.7 articles in geography journals meeting our criteria between 2017 and 2021. 
Roughly one-third (33.0\%) were most recently a corresponding author for an article published in a general geography journal. 
A similar proportion (32.0\%) were most recently a corresponding author for an article published in an earth sciences journal, and smaller proportions had published in the social sciences and cultural geography (20.0\% and 16.0\%, respectively).

\subsection*{Survey Instrument}
The survey first established eligibility based on age and geographic research activity in the past five years and asked researchers to report their primary subfield and methodology.
We asked each participant to assess their familiarity with the term ``reproducibility'' and to provide their own definition. 
We then provided a definition based on the \citet{NASEM2019} to establish a common understanding of reproducibility for the remainder of the survey.
Remaining questions assessed familiarity and use of reproducible research practices (22 questions), perceptions of the reproducibility of geographic research (2 questions), and beliefs about reproducibility with regards to its significance (17 questions) and barriers (13 questions).
For researchers who reported attempting reproductions, we asked researcher to elaborate on their motivations and outcomes (9 questions).

We developed the survey questions following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature. 
We pilot tested the survey instrument with \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
After pilot testing, we removed these individuals from our sampling frame to ensure they would not be included in our final sample.

@@

The online survey was administered through \href{https://www.qualtrics.com/}{Qualtrics}. 
Participation in the survey was entirely voluntary. 
Each researcher that opted to participate in the survey was provided with IRB approved consent documentation and linked to the internet survey instrument. 
Participants were also given the option to provide an email address for eligibility for one of three  prizes of 90 US\$, selected randomly after the data collection period.
Participating researchers had the option to exit and re-enter the survey and were also able to review and change their answers using a back button as they progressed through the survey.
At the end of the data collection period, responses were checked for completeness and coded using the reporting standards of the American Association For Public Opinion Research \citep{aaporstandards}.
Responses were downloaded from Qualtrics, anonymized, and stored in a public de-identified database in the research compendium (self-identifying reference removed).

@@

We conducted two statistical analyses of the survey responses.
First, we analyzed researcher perspectives on reproducibility by coding and calculating summary variables and statistics for three themes: how geographic researchers define reproducibility, familiarity and experience with reproducible research practices, and perceived barriers to reproducibility.
Second, we analyzed researchers' experiences with reproducing prior studies, for those who had done so, including their motivations and experience of successes and barriers.

@@

Second, we coded each definition to one of four motivations for ensuring the reproducibility of a study: (i) to facilitate the assessment of prior work, (ii) assess experimental research, (iii) to improve transparency and facilitate further extension of work, and (iv) to improve the transparency and consistency of data collection.
We derived this coding from common themes in the responses and our own reading of the reproducibility literature.
As above, each definition was independently coded by each author before code assignments across authors were compared with disagreements resolved through discussion.

@@

\textit{Barriers:} Finally, we asked asked respondents to identify how frequently they believe 12 different factors contributed to a lack of reproducibility in the discipline. 
From those responses, we created a measure of perceived barriers by counting the number of factors a researcher believes `frequently' or `occasionally' contributed to irreproducibility, resulting in a measure with domain [0, 12].

To examine variation in researcher understanding of reproducibility across disciplinary subfields and methodological traditions, we cross tabulated these summary measures and responses to individual questions for these subgroups. 
We then compared response frequencies across subgroups.

@@

\textit{Motivations:} To assess what motivated researchers to attempt reproductions, two of the authors independently assigned participants text-based response to groups with the following motivations: i) verify/check published research, ii) learn from published research for extension or teaching, iii) internally check their own research to verify their work and/or increase the transparency of their work, and iv) replicate a study with new data.
We identified disagreements in motivation assignments, and the third author again resolved all disputes in consultation with the two assigning authors.
We selected groups i) and ii) for further analysis of reproduction attempts, as these motivations most closely matched our definition of reproduction.

\textit{Success and Barriers:} To analyze participant success, we create statistical summaries for a series of questions that asked researcher to identify whether they were able to partially or completely recreate some or all results of the target study. 
We similarly analyzed barriers to the reproduction of results by creating statistical summaries of participants' ability to access key study artifacts (e.g., data, procedural information, code).

@@

Strikingly, only 58 percent of respondents believe reproducibility is compatible with the epistemologies used in their disciplinary subfields.
In total, 28 percent of respondents indicated that reproducibility was incompatible with the epistemologies of their subfields, with an additional 12 percent of respondents indicated that they did not know whether reproducibility was epistomologically compatible. 
About half of the respondents specializing in human geography (49\%) and nature and society (50\%) indicated that reproducibility was incompatible with the epistomologies of their subfields. 
Respondents conducting primarily qualitative research were similarly skeptical of the epistemological role of reproducibility in their subfields.
75 percent of qualitative researchers indicated that reproducibility was incompatible with the epistomologies of their subfields.

Table \ref{tab:overview} summarizes how researchers define reproducibility, their familiarity with reproducible research practices and experience using them, and the factors they see as barriers to reproducibility in geography. 
We present the mean and standard deviation for the overall sample and for each subfield and methodological approach.
In aggregate, the data reveal trends in definition, familiarity, experience, and barriers of reproducibility between the sub-disciplines and methodological approaches. 
Respondents that self-identified as specializing in physical geography and geographic methods consistently report higher indicators than those working in nature and society and human geography.
Similarly, respondents that identified as primarily using quantitative and mixed methods approaches consistently report higher indicators than those using qualitative methods.
The following sub-sections present detailed results for each of these topics, highlighting the principal sources of difference between sub-disciplines and methodological approaches.

@@

%%%%%%%%%%%
\subsubsection*{Definitions and Importance of Reproducibility}
A total of 181 (83.0\%) of our survey respondents provided an interpretable definition of reproducibility.  
Geographic researchers provided definitions of reproducibility that explicitly included an average of 1.83 of the four characteristics from the definition adopted by the NASEM.
The availability and use of the same research procedures (80.7\%) and results (74.0\%) were the characteristics of reproducibility most frequently identified by researchers. 
Less than half of respondents explicitly included use of the same data (38.1\%) or the need to work in the same context (17.7\%) in their definitions. 
The pattern of similarity to the NASEM definition and each of its components was consistent across subfields and methodological approaches, with a slightly greater emphasis on data and procedural availability amongst quantitative and methods-focused researchers.
The lower inclusion of data and context in definitions may be explained by researchers conceptualizing reproducibility as the formal NASEM definition of replicability, which emphasizes the testing of similar questions and procedures in new contexts with new data. 
For example, one respondent defines reproducibility as, ``the extent to which the research design can be replicated in different geographical contexts."
We observed this alternative definition of reproducibility in 20.4\% of respondents' definitions.

Researchers' definitions of reproducibility were primarily connected to two epistemic functions.
Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies through comparison of original results to results from an attempted reproduction.
These ranged from rigid bitwise quantitative interpretations, as in the ``ability to re-generate exactly the results published based on the data and code provided by the authors", to more flexible interpretations in which ``other researchers could use the same or similar methodology without great difficulty and, given similar data, arrive at comparable results."
Responses included definitions with a focus on experimental science, as in ``an ability to produce consistent results when an experiment is repeated!"

@@

Qualitative researchers identified reproducibility as playing a much smaller epistemic role compared to the discipline as a whole. 
A majority of the qualitative researchers responded that reproducibility is incompatible with the epistemologies used in their subfield (75.0\%).
Accordingly, a small percentage of qualitative researchers agreed that reproducibility is important for validating research (25.0\%) or establishing its credibility (20.0\%).
Qualitative geographers similarly placed less emphasis on reproducibility as a means of increasing the accessibility and extensibility of research.
Few qualitative researchers had less trust in a study when researchers did not share their data (27.5\%), or saw reproducibility as important for sharing research with academics (27.5\%).

The data from our sample of researchers has shown broad recognition of reproducibility and its importance in geography with three caveats---confusion between reproducibility and replicability, different perspectives from researchers using qualitative methods, and caution about judging the trustworthiness or validity published research based on its reproducibility. 
In this context, are individual researchers aware of the research practices needed to enhance reproducibility, and have these practices already been adopted for use in research?

@@

Researcher familiarity and use of reproducible research practices varied by disciplinary subfield and methodological approach. 
Researchers that identified as physical geographers or methodologists and GIScientists reported being familiar with one to two more reproducible researcher practices than human geographers and those focused on nature and society.
Researcher practices similarly diverged by subfield, but no subset of researchers reported using on average more than two of these practices regularly in their work.  
When grouped by methodological approach, quantitative and mixed-methods researchers on average reported familiarity with and use of two more reproducible research practices when compared to qualitative researchers.

>>>>

\usepackage{doi}
\usepackage{natbib}
%\bibliographystyle{natbib}
\bibliographystyle{chicago}
\setcitestyle{authoryear,open={(},close={)}}
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty

@@

\begin{abstract}
The number of reproduction and replication studies undertaken across the sciences continues to rise, however such studies have not yet become commonplace in geography. 
Existing attempts to reproduce geographic research suggest that many studies cannot be fully reproduced, or are simply missing components needed to attempt a reproduction. 
Despite this suggestive evidence, we have not yet systematically assessed geographers' perceptions of reproducibility or the use of reproducible research practices across the discipline's diverse research traditions; nor have we identified the factors that keep geographers from conducting more reproduction studies.
We address each of these needs by surveying active geographic researchers selected using probability sampling techniques from a rigorously constructed sampling frame.
We identify a clear division in perceptions of reproducibility among geographic subfields. 
We also find varying levels of familiarity with reproducible research practices and a perceived lack of incentives to attempt and publish reproduction studies. 
Despite many barriers to reproducibility and divisions between subfields, we also find common foundations for examining and expanding reproducibility in the field.
These include interest in publishing transparent and reproducible methods, and in reproducing other researchers' studies for a variety of motivations including learning, assessing the internal validity of a study, or extending prior work.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Introduction}
Reproducible research publicly discloses the evidence used to support claims made in prior work, facilitates the independent verification of those claims, and enables the extension of that work by the broader research community \citep{earp2015, nosek2012scientific, Schmidt2009}.
While reproducibility is not a guarantee of scientific or practical usefulness, it does provide a strong basis for the collective evaluation of ideas.
Nonetheless, systematic reviews of published research papers reveal a lack reproducibility \citep{moraila2014measuring, iqbal2016reproducible}; and furthermore, attempts to reproduce published research papers frequently fail \citep{raghupathi2022reproducibility, chang2015economics}.
Previous studies consistently link the irreproducibility of research to inadequate record keeping, opaque reporting, the inaccessibility of research components, and a lack of incentives to share research details or to attempt reproduction studies \citep{ranstam2000fraud, anderson2007normative, NASEM2019}.
Surveys of researchers find that few researchers are attempting to independently reproduce the work of others \citep{baker20161, boulbes2018survey}.
At the same time, a sizable portion of survey respondents report knowing of instances in which researchers engaged in questionable or biased research practices tied to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.

Despite these concerns, the available literature currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically.
This knowledge gap exists because researchers conducting reproducibility assessments and surveys of researcher practices have not defined clear target populations for inference, or used probability sampling techniques structured by well-defined sampling frames that support generalization \citep{NASEM2019}.
Attempts to reproduce published studies typically focus on recreating the results of a small number of studies selected based on topical interest or researcher familiarity \citep{camerer2016evaluating, camerer2018evaluating, open2015estimating}. 
Attempts to catalog reproducible research practices have drawn samples of research papers from archives such as conference paper series, specific journals, or disciplinary repositories \citep{byrne_2017, gundersen2018state, stodden2016enhancing, stodden2018enabling}.
Surveys of researchers have drawn samples from authors in specific journals, members of professional associations, or conference attendees \citep{baker20161}.
All of these sampling frames are convenient, but are not guaranteed to be representative of researchers and research activity in a particular field. 
Surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response, which further complicates their evaluation and use. 
Finally, reproducibility assessments have focused on evaluating the computational components of past studies, such as data and code availability, rather than all aspects of research design and execution.

Reproducibility surveys and reproduction attempts in the geographic literature face these same challenges. 
The few available reproducibility surveys in the discipline have relied on convenience samples drawn from specialist conferences and have only focused on computationally-intensive forms of geographic research \citep{balz2020reproducibility, konkol2019, ostermann2017}. 
The small number of published attempts to reproduce geographic research have similarly focused on the computational reproducibility of conference papers \citep{Nust-AGILE_2018, Nust_AGILE_2020, Nust_AGILE_2021, Nust_AGILE_2022, ostermann2021} or on specific topics such as COVID-19 \citep{Holler2023disability, Kedron2022dimaggio, Kedron2023Beyond, paez2022reproducibility}. 
More recent reproduction attempts by \citet{Kedron2023Beyond} show that the factors hindering the recreation of results and the evaluation of claims likely extend beyond computation into the conceptualization and design of geographic research.

Geographers continue to debate the role of reproduction studies in the discipline \citep{brunsdon2016, goodchild2021Annals, kedron2022replication, kedron2021IJGIS, singleton2016, sui2021, Wainwright2021}, examine the reproducibility of individual studies \citep{Nust_AGILE_2022, ostermann2021}, and build the infrastructure needed to support reproducible research \citep{nust2019, wilson2021, yin2019cybergis, Kedron_Holler_Bardin_Hilgendorf_2022}. 
And yet, we still have not systematically assessed the use of reproducible research practices across the discipline's diverse research traditions, or identified the factors that have hindered geographers from adopting reproducible research practices and conducting reproduction studies. 
Without answers to these questions it is unclear what actions geographers should take if they wish to improve the reproducibility of work in the discipline.

To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of reproducibility, perception of reproducibility in their subfields, familiarity and use of reproducible research practices, and barriers to reproducibility.
To support generalization, we design a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.
In the remainder of this paper, we first present the design of our survey, sampling strategy, and analytical approach. 
We then present the results of our survey, first focusing on researcher perceptions and use of reproducible research practices, and then analyzing researcher experiences attempting to reproduce prior work. 
Finally, we discuss the implications of our survey results and limitation of our work, and conclude by proposing where the geography may go from here and how the discipline may contribute to reproducibility across the sciences.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data and Methods}
Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Reproducibility in Geographic Research project (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
The OSF project connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
All of the results presented in this paper can be independently reproduced using the materials in that repository.
We encourage interested readers to critically evaluate and build on these materials.
Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.

@@

First, beginning at the publication level, we identified journals indexed as either geography or physical geography by the Web of Science's Journal Citation Reports that also had a 5-year impact factor greater than 1.5.
From those journals, we created a database of all articles published between 2017 and 2021.

Second, we used Arizona State University's institutional subscription to the \citet{Scopus} to extract journal information (e.g., subject area), article information (e.g., citation counts), and author information (e.g., corresponding status) for each publication. 
Because our intention was to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = ``Article''} and removed all other publication types (e.g., editorials) from our article database. 
We also removed articles with missing authorship information.

Third, we created a list of researchers and their published articles, focusing on corresponding authors for two reasons.
First, corresponding authorship is one indicator of the level of involvement an individual had in a given work. 
While imperfect, it was the best available indicator in the Scopus database as across journals there is no commonly adopted policy for declarations of author work (e.g., CRediT Statements).
Second, Scopus maintains email contact information for all corresponding authors, which gave us a means of contacting researchers in our sampling frame.
Scopus also maintains a unique identifier for each author (\textit{author-id}) across time, which allowed us to identify authors across publications.

Fourth, we constructed a sampling frame of unique researchers and their most recent email contact information. 
We determined uniqueness by grouping researchers by their \textit{author-id}, and we determined the most recent contact information by selecting records associated with the most recent year of publication. 
For 383 researchers who had two or more distinct emails in the latest year of publication, we removed non-institutional personal email addresses and then selected one of the remaining institutional email address.

Applying these criteria yielded a sampling frame of 29,828 researchers. 
On average, these authors published 2.7 articles in geography journals meeting our criteria between 2017 and 2021. 
Roughly one-third (33.0\%) were most recently a corresponding author for an article published in a general geography journal. 
A similar proportion (32.0\%) were most recently a corresponding author for an article published in an earth sciences journal, and smaller proportions published in the social sciences and cultural geography (20.0\% and 16.0\%, respectively).

\subsection*{Survey Instrument}
The survey first established eligibility based on age and geographic research activity in the past five years and asked researchers to report their primary subfield and methodology.
We asked each participant to assess their familiarity with the term ``reproducibility'' and to provide their own definition. 
We then provided a definition based on the \citet{NASEM2019} to establish a common understanding of reproducibility for the remainder of the survey.
Remaining questions assessed familiarity and use of reproducible research practices (22 questions), perceptions of the reproducibility of geographic research (2 questions), and beliefs about reproducibility with regards to its significance (17 questions) and barriers (13 questions).
For researchers who reported attempting reproductions, we asked them to elaborate on their motivations and outcomes (9 questions).

We developed the survey questions following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature. 
We pilot tested the survey instrument with \textit{n}=19 graduate students and geography faculty with differing levels of experience, disciplinary subfields, and methodological background. 
After pilot testing, we removed these individuals from our sampling frame to ensure they would not be included in our final sample.

@@

The online survey was administered through \href{https://www.qualtrics.com/}{Qualtrics}. 
Participation in the survey was entirely voluntary. 
Each researcher that opted to participate in the survey was provided with IRB-approved consent documentation and linked to the internet survey instrument. 
Participants were also given the option to provide an email address for eligibility for one of three  prizes of 90 USD, selected randomly after the data collection period.
Participating researchers had the option to exit and re-enter the survey and were also able to review and change their answers using a back button as they progressed through the survey.
At the end of the data collection period, responses were checked for completeness and coded using the reporting standards of the American Association For Public Opinion Research \citep{aaporstandards}.
Responses were downloaded from Qualtrics, anonymized, and stored in a public de-identified database in the research compendium.

@@

We conducted two statistical analyses of the survey responses.
First, we analyzed researcher perspectives on reproducibility by coding and calculating summary variables and statistics for three themes: how geographic researchers define reproducibility, familiarity and experience with reproducible research practices, and perceived barriers to reproducibility.
Second, we analyzed researchers' experiences with reproducing prior studies including their motivations and experience of successes and barriers.

@@

Second, we coded each definition to one of four motivations for ensuring the reproducibility of a study: (i) to facilitate the assessment of prior work, (ii) to assess experimental research, (iii) to improve transparency and facilitate further extension of work, and (iv) to improve the transparency and consistency of data collection.
We derived this coding from common themes in the responses and our own reading of the reproducibility literature.
As above, each definition was independently coded by each author before code assignments across authors were compared with disagreements resolved through discussion.

@@

\textit{Barriers:} Finally, we asked asked respondents to identify how frequently they believe 12 different factors contributed to a lack of reproducibility in their subfield. 
From those responses, we created a measure of perceived barriers by counting the number of factors a researcher believes `frequently' or `occasionally' contributed to irreproducibility, resulting in a measure with domain [0, 12].

To examine variation in researcher understanding of reproducibility, we cross tabulated responses to individual questions and these summary measures by disciplinary subfields and methodological traditions. 
We then compared response frequencies across subgroups.

@@

\textit{Motivations:} To assess what motivated researchers to attempt reproductions, two of the authors independently assigned participants text-based response to groups with the following motivations: i) verify/check published research, ii) learn from published research for extension or teaching, iii) internally check their own research to verify their work and/or increase the transparency of their work, and iv) replicate a study with new data.
We identified disagreements in motivation assignments, and the third author again resolved all disputes in consultation with the two assigning authors.
We selected groups i) and ii) for further analysis of reproduction attempts, as these motivations most closely matched the NASEM definition of reproducibility.

\textit{Success and Barriers:} To analyze participant success, we created statistical summaries for a series of questions that asked researchers to identify whether they were able to partially or completely recreate some or all results of the target study. 
We similarly analyzed barriers to the reproduction of results by creating statistical summaries of participants' ability to access key study artifacts (e.g., data, procedural information, and code).

@@

Strikingly, only 58 percent of respondents believe reproducibility is compatible with the epistemologies used in their disciplinary subfield.
An additional 28 percent of respondents reported that reproducibility was incompatible with the epistemologies of their subfields, and  12 percent of respondents indicated that they did not know whether reproducibility was epistemologically compatible. 
About half of the respondents specializing in human geography (49\%) and nature and society (50\%) indicated that reproducibility was incompatible with the epistomologies of their subfields. 
Respondents conducting primarily qualitative research were similarly skeptical of the epistemological role of reproducibility in their subfield.
75 percent of qualitative researchers indicated that reproducibility was incompatible with the epistemologies of their subfield.

Table \ref{tab:overview} summarizes how researchers define reproducibility, their familiarity with reproducible research practices and experience using them, and the factors they see as barriers to reproducibility in geography. 
We present the mean and standard deviation for the overall sample and for each subfield and methodological approach.
In aggregate, the data reveal consistent trends in definition, familiarity, experience, and barriers of reproducibility between the sub-disciplines and methodological approaches. 
Respondents that self-identified as specializing in physical geography and geographic methods consistently report higher indicators than those working in nature and society and human geography.
Similarly, respondents that identified as primarily using quantitative and mixed methods approaches consistently report higher indicators than those using qualitative methods.
The following sub-sections present detailed results for each of these topics, highlighting the principal sources of difference between subfields and methodological approaches.

@@

%%%%%%%%%%%
\subsubsection*{Definitions and Importance of Reproducibility}
A total of 181 (83.0\%) of our survey respondents provided an interpretable definition of reproducibility.  
Geographic researchers provided definitions of reproducibility that explicitly included an average of 1.83 of the four characteristics from the definition adopted by the NASEM.
The availability and use of the same research procedures (80.7\%) and results (74.0\%) were the characteristics of reproducibility most frequently identified by researchers. 
Less than half of respondents explicitly included use of the same data (38.1\%) or the need to work in the same context (17.7\%) in their definitions. 
The pattern of similarity to the NASEM definition and each of its components was consistent across subfields and methodological approaches, with a slightly greater emphasis on data and procedural availability amongst quantitative and geographic methods and GIS researchers.
The lower inclusion of data and context in definitions may be explained by researchers conceptualizing reproducibility as the formal NASEM definition of replicability, which emphasizes the testing of similar questions and procedures in new contexts with new data. 
For example, one respondent defines reproducibility as, ``the extent to which the research design can be replicated in different geographical contexts."
We observed this alternative definition of reproducibility in 20.4\% of respondents' definitions.

Researchers' definitions of reproducibility were primarily connected to two epistemic functions.
Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies through comparison of original results to results from an attempted reproduction.
These comparisons ranged from rigid bitwise quantitative interpretations, as in the ``ability to re-generate exactly the results published based on the data and code provided by the authors", to more flexible interpretations in which ``other researchers could use the same or similar methodology without great difficulty and, given similar data, arrive at comparable results."
Responses included definitions with a focus on experimental science, as in ``an ability to produce consistent results when an experiment is repeated!"

@@

Qualitative researchers identified reproducibility as playing a much smaller epistemic role compared to the discipline as a whole. 
A small percentage of qualitative researchers agreed that reproducibility is important for validating research (25.0\%) or establishing its credibility (20.0\%).
Qualitative geographers similarly placed less emphasis on reproducibility as a means of increasing the accessibility and extensibility of research.
Few qualitative researchers had less trust in a study when researchers did not share their data (27.5\%), or saw reproducibility as important for sharing research with academics (27.5\%).

The data from our sample of researchers has shown broad recognition of reproducibility and its importance in geography with three caveats---confusion between reproducibility and replicability, different perspectives from researchers using qualitative methods, and caution about judging the trustworthiness or validity of published research based on its reproducibility. 
In this context, are individual researchers aware of the research practices needed to enhance reproducibility, and have these practices already been adopted for use in research?

@@

Researcher familiarity and use of reproducible research practices varied by disciplinary subfield and methodological approach. 
Researchers that identified as physical geographers or methodologists and GIScientists reported being familiar with one to two more reproducible research practices than human geographers and those focused on nature and society.
Researcher practices similarly diverged by subfield, but no subset of researchers reported using on average more than two of these practices regularly in their work.  
Quantitative and mixed-methods researchers reported familiarity with and use of an average of two more reproducible research practices when compared to qualitative researchers.

Differences in researcher familiarity and use of specific reproducible research practices across subfields and approaches was greatest for practices more typical of quantitative workflows. 
When compared to qualitative researchers, quantitative and mixed-methods researchers reported greater familiarity with all reproducible research practices.
For example, just 12.5 percent of qualitative researchers reported familiarity with code sharing, while 81.5 percent of quantitative and 57.7 percent of mixed-methods researchers reported familiarity with the same practice.
However, even among quantitiative and mixed-methods researchers, familiarity with reproducible research practices did not translate into regular use of those practices.
Just over half of quantitative and mixed-methods researchers reported regularly sharing their data.
Less than a quarter of these same researchers reported regularly sharing their code. 
These rates were lower for qualitative geographers, of which only a small subset reported using open source software or field notes, or sharing data and code most of the time or always.

\subsubsection*{Perceived Barriers to Reproducible Research}
Aligning with the differences we observed between researcher familiarity with reproducibility enhancing research practices and researcher use of those same practices, respondents to our survey identified an average of 8.20 factors contributing to a lack or reproducible research. 
Geographic researchers working in different subfields and with different methodological approaches each identified a similar number of barriers to reproducibility, as shown in Table \ref{tab:barriers}.
Qualitative geographers may be the one group that deviates from this consistent pattern. 
These researchers identified fewer barriers to reproducibility on average, but with a greater variance that left us unable to distinguish this group from any other.
To examine differences in the specific factors researchers believe hinder reproducibility in the discipline, we divided the 12 factors into three groups---those related to the research environment, the availability of research artifacts, and study-specific characteristics.
